---
title: "SPEI Data"
author: "Kenny Joseph"
date: "December 11, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Required packages.
```{r, include=FALSE}
require(plyr)
require(dplyr)
require(tidyr)
require(ggplot2)
require(ggpubr)
require(zoo)
require(reshape2)
require(readxl)
require(SPEI)
require(hydroTSM)
```

List of GCMs(global climate models) used.
```{r}
#canesm2, ccsm4, cesm1-bgc, cmcc-cms, cnrm-cm5, csiro-mk3-6-0, gfdl-cm3, gfdl-esm2g, hadgem2-cc, hadgem2-es, inmcm4, miroc5, mpi-esm-lr, mri-cgcm3, norems1-m
#canesm2, ccms4, cesm1-bgc, cmcc-cms, cnrm-cm5, gfdl-cm3, hadgem2-cc, hadgem2-es, miroc5
gcm<-"miroc5"
```

Reading in the Data for rainfall and potential evapotranspiration.
```{r}
rainfall<-read.zoo(paste("D:/RStudio/Climate Change/BCSD_daily_3/loca_daily_meteorology/",gcm,"_rcp85_pr_stn_77.txt", sep=""))
evapotrans<-read.zoo(paste("D:/RStudio/Climate Change/EvapoTrans/",gcm,"_rcp85_pet_natveg_stn_77_daily.txt",sep=""))
speidata<-rainfall-evapotrans
```

General housekeeping, turning the data into monthly data, and rounding all of the numbers to the first decimal place (just for everything to look cleaner)
```{r}
names(speidata)=c("Date","Data")
newdata<-daily2monthly(speidata, FUN=sum, na.rm=TRUE)
newdata2<-data.frame(newdata)
newdata2[,2]<-rownames(newdata2)
newdata2[,3]<-newdata2[,1]
newdata2<-newdata2[-1]
newdata2<-data.frame(newdata2, row.names=NULL)
newdata2[,3]<-rep(c("January","Febuary","March","April","May","June","July","August","September","October","November","December"),150)
newdata2[,2]<-round(newdata2[,2], digits=1)
```

Adding the years into the data frame (12x1950, 12x1951, etc)
```{r}
x<-1950:2099
for (i in 1:150)
{
  newdata2[i*12-11,4]<-x[i]
  newdata2[i*12-10,4]<-x[i]
  newdata2[i*12-9,4]<-x[i]
  newdata2[i*12-8,4]<-x[i]
  newdata2[i*12-7,4]<-x[i]
  newdata2[i*12-6,4]<-x[i]
  newdata2[i*12-5,4]<-x[i]
  newdata2[i*12-4,4]<-x[i]
  newdata2[i*12-3,4]<-x[i]
  newdata2[i*12-2,4]<-x[i]
  newdata2[i*12-1,4]<-x[i]
  newdata2[i*12,4]<-x[i]
}
```

Creating a new data frame that can run in the SPEI package. The data frame needs a year, a month, and a values column.
```{r}
data1<-data.frame(matrix(nrow=12, ncol=151))
data1[,1]<-c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec")

for (i in 1:150)
{
  for (j in 1:12)
  {
    data1[j,i+1]<-newdata2[(j+12*i-12),2]
  }
}
names(data1)<-c("Months",1950:2099)
newdata3<-data.frame(matrix(nrow=1800,ncol=1))
newdata3[,1]<-newdata2[,4]
newdata3[,2]<-c(rep(1:12,150))
newdata3[,3]<-newdata2[,2]
names(newdata3)<-c("YEAR","MONTH","PRCP")
spidata<-spei(newdata3$PRCP, scale=36, distribution = 'log-Logistic')
```

The plot of the SPEI data.
```{r}
plot(spidata)
```

Important values to note.
```{r, include=FALSE}
a<-data.frame(print(spidata))
c<-c(a[,1])
trends<-as.integer(ifelse(c<0,0,1))
zero<-length(which(trends==0))
ones<-length(which(trends==1))
trends1<-as.integer(ifelse(c< -1,0,1))
zero1<-length(which(trends1==0))
trends2<-as.integer(ifelse(c>1,0,1))
ones1<-length(which(trends2==0))
```

ts[cont]<-mean(c[cont]:c[(cont+599)], na.rm=TRUE)
```{r}
ts<-rep(0,1201)
ts1<-rep(0,600)
for (cont in 36:1201)
{
  ts1<-c[cont:(cont+599)]
  counting<-sum(ts1< (-1))
  ts[cont]<-counting
}
ts<-ts[37:1201]/12
```



```{r}
time<-seq(1978,2075, by=1/12)
timeseries<-data.frame(time, ts)
tsplot<-ggplot(timeseries, aes(x=time, y=ts))+geom_point()+theme_bw()+
  geom_abline(intercept=106.58960, slope=-0.04772)+
  scale_x_continuous(breaks = seq(1975,2075, by=10),limits=c(1978,2075),expand=c(0,0))+
  scale_y_continuous(breaks = seq(0,20, by=2),limits=c(0,20),expand=c(0,0))+
  geom_hline(yintercept=0)+xlab("Year")+ylab("Number of Drought Years")
tsplot

```




